Manuscript Figures for Genome Biology

### 2018-06-06 manuscript_figures/manuscript_figures.Rmd
Fix typo in save of Alt Supp Figure
Adjust margins of Fig S7

pa <- plotsim_average(res5n_u, met="TNR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) +
        expand_limits(y=.7) +
        xlab("") +
        ggtitle("")

pb <- plotsim_average(res5n, met="TNR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) +
        theme(legend.position="none", plot.title = element_text(hjust = 0.5))+
        expand_limits(y=.7) +
        xlab("") +
        ggtitle("")

pc <- plotsim_average(res5d_u, met="FDR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) +
        theme(legend.position="none") +
        expand_limits(y=0.2) +
        xlab("") +
        ggtitle("")

pd <- plotsim_average(res5d, met="FDR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) +
        theme(legend.position="none") +
        expand_limits(y=0.2) +
        xlab("") +
        ggtitle("")

pe <- plotsim_average(res5d_u, met="TPR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) +
        theme(legend.position="none") +
        expand_limits(y=0.33) +
        ggtitle("")

pf <- plotsim_average(res5d, met="TPR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) +
        theme(legend.position="none") +
        expand_limits(y=0.33) +
        ggtitle("")

@@

ggsave(file.path(outdir, "FigureSAlt.pdf"), gp, width = 12, height = 5)
```

>>>>

pa <- plotsim_average(res5n_u, met="TNR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) +
        expand_limits(y=0.93) +
        xlab("") +
        ggtitle("")

pb <- plotsim_average(res5n, met="TNR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) +
        theme(legend.position="none", plot.title = element_text(hjust = 0.5))+
        expand_limits(y=.93) +
        xlab("") +
        ggtitle("")

pc <- plotsim_average(res5d_u, met="FDR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) +
        theme(legend.position="none") +
        expand_limits(y=0.18) +
        xlab("") +
        ggtitle("")

pd <- plotsim_average(res5d, met="FDR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) +
        theme(legend.position="none") +
        expand_limits(y=0.18) +
        xlab("") +
        ggtitle("")

pe <- plotsim_average(res5d_u, met="TPR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) +
        theme(legend.position="none") +
        expand_limits(y=c(0.10,0.55)) +
        ggtitle("")

pf <- plotsim_average(res5d, met="TPR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) +
        theme(legend.position="none") +
        expand_limits(y=c(0.10,0.55)) +
        ggtitle("")

@@

ggsave(file.path(outdir, "FigureSAlt.pdf"), SFigAlt, width = 12, height = 5)
```
